\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-30 paper/subdocuments/methods.Rnw
switched coefplot to bmp for performance and corrected latex error

The second approach investigates whether the FTA time series is suitable to analyze trends of inequality even if the inequality measures are biased. We can do this by regressing the inequality measure (here the Gini coefficient) on the share of zeros. Simply spoken we test if cutting a larger (left) tail of the distribution changes the shape of the distribution. We include Gini coefficient for all cantons in our analyses to improve the power of our statistical test\footnote{Furthermore without cantonal data (but only data for aggregate Switzerland) it is impossible to distinguish whether inequality changed due to the number of unobserved people or any other variable that changed over time).

<<corrected_gini>>=
df$J<-factor(df$steuerperiode)
fit <- lm(G_steink~kanton+kanton:zeros+J+zeros:J,data=df)
#summary(fit)
SmoothCoefficientPlot <- function(models, modelnames = "", removeintercept = FALSE){
  # models must be a list()

@@

library(grid) #for arrow() function
SmoothCoefficientPlot(fit,modelnames=paste0("By cantons: Impact of the share of zeros on inequality (Gini) Rsq=", round(summary(fit)$r.squared,2)))+geom_text(show_guide=FALSE,x=77,y=2.2,size=4,label="effect variation\nover time")+geom_segment(aes(x = 85, y = 1.5, xend = 71, yend = 1.5))+geom_segment(aes(x = 71, y = 1.5, xend = 71, yend = 1.3))+geom_segment(aes(x = 85, y = 1.5, xend = 85, yend = 1.3))+geom_text(show_guide=FALSE,x=57,y=1.9,size=4,label="effect variation\nby cantons")+geom_segment(aes(x = 71, y = 1.2, xend = 45, yend = 1.2))+geom_segment(aes(x = 71, y = 1.2, xend = 71, yend = 1.0))+geom_segment(aes(x = 45, y = 1.2, xend = 45, yend = 1.0))+ggtitle("Bias variation by time and cantons")

>>>>

The second approach investigates whether the FTA time series is suitable to analyze trends of inequality even if the inequality measures are biased. We can do this by regressing the inequality measure (here the Gini coefficient) on the share of zeros. Simply spoken we test if cutting a larger (left) tail of the distribution changes the shape of the distribution. We include Gini coefficient for all cantons in our analyses to improve the power of our statistical test\footnote{Furthermore without cantonal data (but only data for aggregate Switzerland) it is impossible to distinguish whether inequality changed due to the number of unobserved people or any other variable that changed over time)}.

<<corrected_gini, dev='bmp'>>=
df$J<-factor(df$steuerperiode)
fit <- lm(G_steink~kanton+kanton:zeros+J+zeros:J,data=df)
#summary(fit)
SmoothCoefficientPlot <- function(models, modelnames = "", removeintercept = FALSE){
  # models must be a list()

@@

library(grid,quietly=TRUE, warn.conflicts=FALSE) #for arrow() function
SmoothCoefficientPlot(fit,modelnames=paste0("By cantons: Impact of the share of zeros on inequality (Gini) Rsq=", round(summary(fit)$r.squared,2)))+geom_text(show_guide=FALSE,x=77,y=2.2,size=4,label="effect variation\nover time")+geom_segment(aes(x = 85, y = 1.5, xend = 71, yend = 1.5))+geom_segment(aes(x = 71, y = 1.5, xend = 71, yend = 1.3))+geom_segment(aes(x = 85, y = 1.5, xend = 85, yend = 1.3))+geom_text(show_guide=FALSE,x=57,y=1.9,size=4,label="effect variation\nby cantons")+geom_segment(aes(x = 71, y = 1.2, xend = 45, yend = 1.2))+geom_segment(aes(x = 71, y = 1.2, xend = 71, yend = 1.0))+geom_segment(aes(x = 45, y = 1.2, xend = 45, yend = 1.0))+ggtitle("Bias variation by time and cantons")
